%-------------------------
 % Resume in Latex
 % Author : Chirag Khandhar
 % License : MIT
 %------------------------

 \documentclass[letterpaper,11pt]{article}

 \usepackage{latexsym}
 \usepackage[empty]{fullpage}
 \usepackage{titlesec}
 \usepackage{marvosym}
 \usepackage[usenames,dvipsnames]{color}
 \usepackage{verbatim}
 \usepackage{enumitem}
 \usepackage[hidelinks]{hyperref}
 \usepackage{fancyhdr}
 \usepackage[english]{babel}
 \usepackage{tabularx}
 \input{glyphtounicode}


 %----------FONT OPTIONS----------
 % sans-serif
 % \usepackage[sfdefault]{FiraSans}
 % \usepackage[sfdefault]{roboto}
 % \usepackage[sfdefault]{noto-sans}
 % \usepackage[default]{sourcesanspro}

 % serif
 % \usepackage{CormorantGaramond}
 % \usepackage{charter}


 \pagestyle{fancy}
 \fancyhf{} % clear all header and footer fields
 \fancyfoot{}
 \renewcommand{\headrulewidth}{0pt}
 \renewcommand{\footrulewidth}{0pt}

 % Adjust margins
 \addtolength{\oddsidemargin}{-0.5in}
 \addtolength{\evensidemargin}{-0.5in}
 \addtolength{\textwidth}{1in}
 \addtolength{\topmargin}{-.5in}
 \addtolength{\textheight}{1.0in}

 \urlstyle{same}

 \raggedbottom
 \raggedright
 \setlength{\tabcolsep}{0in}

 % Sections formatting
 \titleformat{\section}{
   \vspace{-4pt}\scshape\raggedright\large
 }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

 % Ensure that generate pdf is machine readable/ATS parsable
 \pdfgentounicode=1

 %-------------------------
 % Custom commands
 \newcommand{\resumeItem}[1]{
   \item\small{
     {#1 \vspace{-2pt}}
   }
 }

 \newcommand{\resumeSubheading}[4]{
   \vspace{-2pt}\item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
       \textbf{#1} & #2 \\
       \textit{\small#3} & \textit{\small #4} \\
     \end{tabular*}\vspace{-7pt}
 }

 \newcommand{\resumeSubSubheading}[2]{
     \item
     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
       \textit{\small#1} & \textit{\small #2} \\
     \end{tabular*}\vspace{-7pt}
 }

 \newcommand{\resumeProjectHeading}[2]{
     \item
     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
       \small#1 & #2 \\
     \end{tabular*}\vspace{-7pt}
 }

 \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

 \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

 \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
 \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
 \newcommand{\resumeItemListStart}{\begin{itemize}}
 \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

 %-------------------------------------------
 %%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


 \begin{document}

 %----------HEADING----------


 \begin{center}
     \textbf{\Huge \scshape Chirag Khandhar} \\ \vspace{1pt}
     \small XXX-XXX-XXXX $|$ \href{mailto:abc@zyx.com}{\underline{abc@zyx.com}} $|$ 
     \href{https://www.linkedin.com/in/chirag-khandhar/}{\underline{linkedin.com/in/chirag-khandhar}} $|$
     \href{https://github.com/chiragkhandhar}{\underline{github.com/chiragkhandhar}}
 \end{center}


 %-----------EDUCATION-----------
 \section{Education}
   \resumeSubHeadingListStart
     \resumeSubheading
       {Illinois Institute of Technology }{Chicago, IL}
       {Master of Computer Science |\textbf{ GPA: 3.66}}{May 2021}
           \resumeItemListStart
             \resumeItem{Top Courses: Enterprise Web Applications, Mobile Application Development, Geo-spatial Vision and Visualization, Software Systems Architecture, Software Modelling  }
         \resumeItemListEnd

   \resumeSubHeadingListEnd

 %-----------EXPERIENCE-----------
 \section{Experience}
   \resumeSubHeadingListStart

     \resumeSubheading
       {Software Engineer}{June 2021 – Present}
       {Egen Solutions}{Chicago, IL}
       \resumeItemListStart
         \resumeItem{Developed a cross-platform mobile app, using \textbf{Ionic}, to make end-to-end SSL secured payments for a car loan, that channelize \textbf{\$1B} in annual revenue.}
         \resumeItem {Tech-design and develop high value features like\textbf{ Auto-Pay} to automate payments through bank accounts.}
         \resumeItem{Developed Angular Services to simplify Apollo \textbf{state-management}, \textbf{mutations} and \textbf{querying} operations.}
            \resumeItem{Built pixel perfect \textbf{ADA compliant} UI components, dashboards and workflows for the app, in a TDD env.}
          \resumeItem{Write Unit \& Integration tests with Jasmine \& CyPress respectively covering functional requirements to maintain code-quality.}
 		\resumeItem{Participate in Regression Testing, UAT/PROD support for fixing priority issues.}
         \resumeItem{Own feature deployments by build-mastering it }
         \resumeItem{Open-source contributions to the Ionic Framework  (v6) by identifying and creating issues.}
         \resumeItem {Technologies: TypeScript, Angular 12, Capacitor 3, Ionic 6, CyPress, Jasmine, Apollo, GraphQL, RxJS, SwiperJS, Lodash, Auth0, Launch Darkly, PaymentUs, Azure Devops.}
       \resumeItemListEnd

     \resumeSubheading
       {Graduate Research Assistant}{January 2021 – May 2021}
       {Department of Energy, Argonne National Laboratory}{Chicago, IL}
       \resumeItemListStart
         \resumeItem{Developed a web framework for building a real-time layered map interface that assists power companies to visualize \& monitor power-grid infrastructure.}
         \resumeItem{Utilized \textbf{LeafletJS} and \textbf{MapboxGL} to render \& control multiple tiled layers and \textbf{GeoJSON} data points.}
         \resumeItem{Product, UX and UI designed the web framework by translating requirements from the computational scientists.}
         \resumeItem{Technologies: JavaScript, LeafletJS, GeoJSON, TileMill, AWS EC2, Docker, Figma, Python.}
       \resumeItemListEnd

     \resumeSubheading
       {Software Engineer Intern}{September 2020 – December 2020}
       {Scripted Team, Script Health}{Chicago, IL}
       \resumeItemListStart
         \resumeItem{Built a SAAS product, that enables pharmacists to prescribe for common treatments \& conditions.}
         \resumeItem{Designed and implemented clinical review dashboard to render self-assessed forms of 10+ common conditions.  }
         \resumeItem{Developed high value experiences like User On-boarding, Clinical Review, 2-FA and Admin Settings Panel.  }
         \resumeItem{Technologies: JavaScript, \textbf{React, React Hooks}, \textbf{Redux}, MaterialUI, JEST, JIRA, Bitbucket.}
       \resumeItemListEnd

     \resumeSubheading
       {Software Engineer Intern}{May 2020 – August 2020}
       {Knobull Inc}{Chicago, IL}
       \resumeItemListStart
         \resumeItem{Built  a web app using \textbf{Mongo-Express-React-Node}  that assists researchers to ask \& answer questions.}
         \resumeItem{Developed UI components, REST API endpoints and middleware with a continuous deployment over Heroku. }
         \resumeItem{Enabled Google \textbf{O-Auth} log-in and sign-up experience using \textbf{PassportJS}.    }
       \resumeItemListEnd

     \resumeSubHeadingListEnd

 %-----------COMMUNITY AND LEADERSHIP-----------
 \section{Community \& Leadership}
   \resumeSubHeadingListStart
      \resumeSubheading
       {Open Source Contributor }{June 2021 – Present}
       {Ionic Framework | Egen Solutions }{Chicago , IL}

     \resumeSubheading
       {Creative Head}{September 2019 – December 2020}
       {Indian Student Association | Illinois Institute of Technology }{Chicago , IL}
     \resumeSubHeadingListEnd


 %-----------TECHNICAL SKILLS-----------
 \section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
     \small{\item{
      \textbf{Languages}{: TypeScript, Java, Python, SASS} \\
      \textbf{Frameworks}{: Angular, Ionic, React, NodeJS, Jasmine, Jest} \\
      \textbf{Libraries}{: Apollo, Lodash, Redux, MaterialUI, LeafletJS, MapboxGL, ExpressJS, Charts.JS, PassportJS } \\
      \textbf{Developer Tools}{: Git, Bitbucket, JIRA, TargetProcess, Zeplin, Fork, JsDoc, VS Code, IntelliJ IDEs, Postman, Mapbox Studio} \\

     }}
  \end{itemize}


 %-------------------------------------------
 \end{document}